Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-09-15 fib2.tex
outline of supp material
more pictures. anyons are still red.

@@

The sollid lines represent Fibonacci world-lines.
The dotted lines represent vacuum charges,
and we are free to include these lines or not.
The non-trivial $R$-moves are:
\begin{align*}
\includegraphics[]{pic-skein2.pdf}
\end{align*}

@@

Here we show a process where a 
Fibonacci anyon travels around the torus and
anihilates itself. Twice.
The vertical lines represent a periodic
identification, and we leave anyons paths
as undirected because Fibonacci anyons are
self-inverse.
\begin{align*}
\includegraphics[]{pic-logops.pdf}
\end{align*}

@@

\section{Details on the simulation algorithm}

>>>>

We give an informal introduction to
the easy (picture) topological quantum
field theory in $(2+1)$-dimensions.
Note that these theories give rise to
\emph{doubled} anyonic charges, and so
the example in the main text only simulates
one half of such a system...

\section{Interaction picture}

In two spacial dimensions, particle exchange is
captured by the braid group.
World lines of such particles 
become tangled (braided) in $(2+1)$-dimensions.
For example, three particle statistics is captured
by the braid group on three strands $B_3.$
This group is generated by elements $\sigma_1$
and $\sigma_2$ which we represent pictorially as:
\begin{center}
\includegraphics[]{pic-braid-group.pdf}
\end{center}

These pictures make clear how the group
multiplication works, for example:
\begin{center}
\includegraphics[]{pic-braid-group-1.pdf}
\end{center}
\begin{center}
\includegraphics[]{pic-braid-relation.pdf}
\end{center}

Braid group acts (naturally) on states.

These diagrams are to be understood up to
continuous deformation of the ambient space.
That is, we allow the ambient $(2+1)$-dimensional
space with these worldlines subtracted to be continuously
deformed.
At the top and bottom of this space is 
a $2$-dimensional space (a disc) with holes in it.
Such a closed disc with $n$ holes we denote as $D_n.$
So this is how we arrive at modelling the system as
a disc with holes in it.
The observables of the system measure charge within
a region bounded by a directed closed curve.
\begin{center}
\includegraphics[]{pic-observable.pdf}
\end{center}

The defining feature of an Abelian anyon theory
is that the state is completely determined once
we measure the charge of each hole.
In the language of the toric code (homology),
logical operators (1-chains)
cancel where they overlap
with opposite orientation:
\begin{center}
\includegraphics[width=0.7\columnwidth]{pic-abelian.pdf}

\end{center}

This is not at all the case in general;
for non-Abelian theories there can be extra
degrees of freedom associated with these
observables. For example, in
the Fibonacci anyon case
\begin{center}
\includegraphics[]{pic-fusion.pdf}
\end{center}
so the state space of two fibonacci anyons
is $2$-dimensional.
Such a space assocated with observing total charge
of multiple anyons is called the \emph{fusion} space
of those charges.

These observables satisfy various relations,
but in particular, non-overlapping observables commute.
So if we nest a maximal set of these observables together
we can pin-down a basis for the fusion space.
Such a nesting is tree-like, and if we confuse the distinction
between holes and observables, this gives rise to the
fusion tree notation.
\begin{center}
\includegraphics[]{pic-tree-0.pdf}\includegraphics[]{pic-tree-1.pdf}
\end{center}

\section{Combinatorial curve diagrams}

We use curve diagrams...
Combinatorial formulation...

\section{Simulation algorithm}

@@

The sollid lines represent Fibonacci world-lines.
The dotted lines represent vacuum charges,
and we are free to include these lines or not.
We leave these anyon paths
as undirected because Fibonacci anyons are
self-inverse.
The non-trivial $R$-moves are:
\begin{align*}
\includegraphics[]{pic-skein2.pdf}
\end{align*}

@@

Here we show a process where a 
Fibonacci anyon travels around the torus and
anihilates itself. Twice.
The vertical lines represent a periodic
identification.
\begin{align*}
\includegraphics[]{pic-logops.pdf}
\end{align*}

@@
